Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
pass through 3

We will introduce a formal model of stack safety that abstracts over
machine details. But first we must discuss the bounds of our assumptions ---
how broadly we can abstract over machines, how we represent enforcement, and
our threat model.

We adopt a strong threat model in which both caller and callee may execute
arbitrary machine code. But hardware and timing attacks are out of scope, as are
are attacks on the heap---though we believe that the work of
\citet{DBLP:conf/post/AmorimHP18} can be combined smoothly with ours
to protect both stack and heap.

@@

That said, our model is meant to apply generically to any enforcement mechanism,
including those that do not take advantage of this separate.
Some mechanisms, like hardware capability systems, might exhibit failstop behavior,
but have no protected policy state --- this is represented by a ``unit'' policy
that failstops when the hardware fault. Others might never even failstop, such as
code rewriting techniques that turn stack safety violations into other (erroneous, but not
stack-unsafe) behaviors. Then the policy-enhanced machine is identical to the original.
\sna{I'm thinking of SFI here, but that's not stacks, right? Does Softbound work like
  this.}

>>>>

Before introducing our formal model of stack safety, we describe our assumptions:
how broadly we can abstract over machines, how we represent enforcement, and
our threat model.

We adopt a strong threat model in which both caller and callee may execute
arbitrary machine code. \apt{But don't they need to be well-formed?? In which case,
  this should go at the end of the section, after that has been explained. [Earlier
    I was only arguing for the explanatory background to be placed earlier, not
    the actual statement of the threat model.]} But hardware and timing attacks are out of scope, as are
are attacks on the heap---though we believe that the work of
\citet{DBLP:conf/post/AmorimHP18} can be combined smoothly with ours
to protect both stack and heap.

@@

That said, our model is meant to apply generically to any enforcement mechanism,
including those that do not take advantage of this separation.
Some mechanisms, like hardware capability systems, might exhibit failstop behavior,
but have no protected policy state---this is represented by a trivial policy
that failstops when the hardware faults. Others might never even failstop, such as
code rewriting techniques that turn stack safety violations into other (erroneous, but not
stack-unsafe) behaviors. Then the policy-enhanced machine is identical to the original.
\sna{I'm thinking of SFI here\apt{yes}, but that's not stacks, right? Does Softbound work like
  this.\apt{dunno}}
